Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-04-18 Paper/Paper.tex

An important, and heavily debated, aspect of the implementation of EHRs is whether or not they increase productivity in users. A main purpose of the HITECH Act was to improve efficiency of care, specifically to decrease time spent on administrative burden. Such a decrease implies a change in patient care: either more patients have access to an appointment, or the same amount of patients receive more face-to-face time with physicians during appointments. In this section, I estimate the effect of EHR implementation on a physician's number of patients seen.

>>>>

An important, and heavily debated, aspect of the implementation of EHRs is whether or not they allow users to be more productive. A main purpose of the HITECH Act was to improve efficiency of care, specifically to decrease time spent on administrative burden. Such a decrease implies a change in patient care: either a larger number of patients have access to an appointment, or the same amount of patients receive more face-to-face time with physicians during appointments. Alternatively, because the technology is not hugely user friendly, it may not decrease administrative burden after all. In this section, I address EHRs' effect on productivity by estimating its effect on a physician's number of patients seen.
